---
title: "Installation instruction for mixKernel"
author: "Jérôme Mariette, Céline Brouard, Rémi Flamary and Nathalie Vialaneix"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    code_folding: show
    highlight: haddock
    df_print: kable
---

<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Installation instruction}
%\VignettePackage{mixKernel}
-->

This vignette provide installation for `mixKernel` instructions. 

## Installation of python dependencies

The following python modules are required for the functions performing 
feature selection in `mixKernel`: autograd, scipy, sklearn, numpy

```{python installModule, eval=FALSE}
pip3 install autograd
pip3 install scipy
pip3 install sklearn
pip3 install numpy
```

## Installation of Bioconductor dependencies

Two Bioconductor packages are required for `mixKernel` installation: `mixOmics`
and `phyloseq`:
```{r installBioc, eval=FALSE}
install.packages("BiocManager")
BiocManager::install("mixOmics")
BiocManager::install("phyloseq")
```

## mixKernel installation

Finally the installation is completed with:
```{r install, eval=FALSE}
install.packages("mixKernel")
```

